Revisiting Multi-Domain Machine Translation

### 2020-04-17 2020/coling2020/multidomain.tex
review related work - we still miss a couple of results, the conclusions and abstract

\section{Requirements of multi-domain MT \label{sec:requirements}}
In this section, we try to recap the main reasons for considering a multi-domain scenario and discuss their implications in terms of performance evaluation.
\fyTodo{Relation to theory, discussion of worst case scenario}
\fyTodo{Insist on the work of Dredze}

Multi-domain learning, as defined in \cite{Dredze08online} additionally makes the requirement that categorial domain tags are available in training and testing; a multi-domain learner should use them effectively \cite{Joshi12multidomain} to improve simultaneously on all domains \cite{Finkel09hierarchical}. This is also the view that we adopt here, where we assume training inputs in $(\mathcal{X}\times{}\{1\dots{}D\})$, sampled from a mixture $\sum \lambda_{s,d}\mathcal{D}_{d} \times \{d\}$, and also consider various test scenarios, depending whether $\mathcal{D}_t$ is a fixed mixture of known domains, include new domain(s), in the supervised and unsupervised, and zero-shot settings.\fyTodo{explain zero shot}.

% ----
\subsection{Formalizing multi-domain translation \label{ssec:formalization}}

@@

A typical learning scenario in MT is to have access to a samples from $n_d$ domains, which means that the training distribution $\mathcal{D}^s$ is a mixture $\mathcal{D}^s(x) = \sum_d \lambda^{s}_{d} \mathcal{D}_d(x)$. Multi-domain learning, as defined in \cite{Dredze08online} further assumes that domain tags are also available in testing; the implication being that the test distribution is also as a mixture $\mathcal{D}^t(x) = \sum_d \lambda^{t}_{d} \mathcal{D}_d(x)$ of several domains, making the problem distinct from mere domain adaption.  A multi-domain learner is then expected to use these tags effectively \cite{Joshi12multidomain} when computing the combined translation function $h(x,d)$, and to perform well in all domains \cite{Finkel09hierarchical}. Note that this setting is closely related to the multi-source adaptation problem studied in \cite{Mansour09domainadaptation,Mansour09multiple}.

This definition seems to be the most accepted view of a multi-domain MT\footnote{One important exception is \cite{Farajian17multidomain}, where test translations rely on a similarity scores between test and train sentences, rather than on domain labels.}, and one that we also adopt here. Note that in the absence of further specification, the naive answer to the MD setting should be to estimate one translation function $\hat{h}_d(x)$ separately for each domain, then to translate using $\hat{h}(x,d) = \sum_{d'} h_{d'}(x) \indic{d' = d}$, where $\indic{x}$ is the indicator function. We now discuss the arguments that are usually put forward to proceed differently.
% --

@@

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training. Such scenario is already well documented for zero-shot multi-lingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}, where mixing languages has more than demonstrated its usefulness.  An even more challenging case is when the MT would need to perform well for any test distribution (as considered eg.\ in \cite{Hoffman18algorithms,Oren19distributionally}  for other tasks). In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected inputs.

@@

% \cite[eq. (3)]{Wang20general} defines the loss of MDMT as the (macro) average of domain loss - all domains are equally important.

\section{Challenging multi-domain translation systems \label{sec:challenging}}
In this section, we discuss seven\fyTodo{check number} operational requirements that can be expected from an effective multi-domain system, and discuss ways to evaluate whether these requirements are actually met. All these evaluations will rest on comparison of translation performance, and do not depend on the choice a particular metrics. To make our results comparable with the literature, we will only use the BLEU score \cite{Papineni02bleu} in Section~\ref{sec:experiments}, noting it may not be the best choice to measure subtle improvements of lexical choices that are often associated with domain adapted systems \cite{Irvine13measuring}. Other important figure of merits for MDMT systems are the computational cost and the total number of parameters.\fyDone{Insert discussion about scores}

@@

We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \cite{Papineni02bleu}.\fyDone{A word about meta-parameter settings}, computed with\fyTodo{}. Significance tests are performed using the bootstrap resampling method of \newcite{Koehn04statistical} and implementation of compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \cite{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value}

@@

\begin{table}
  \centering
  \begin{tabular}{|p{2.5cm}|*{9}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & Wrong \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{bank} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} & domain \\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_1$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law} & \\
    \system{FT-Full}      & -0.13 & -0.6 & -1.51& -0.25& & &\SW{-1.6} & \SW{-1.4}& \\
    \system{DC-Tag}     & -0.16 & -0.27& +0.13& +0.2& & & -0.5 & -0.4 & \\
    \system{DC-Feat}    & -0.47& 0.0 & \SB{0.27} $^+$ & +0.27 $^+$& & & 0.3 & 0.1 & \\
    \system{TTM}          & & & & & & &  0.0 & -0.3 &  \\
    \system{LDC-Tag}   & & & & & & &  0.0 & 0.1& \\ 
    \system{MDL Res}   & -0.2$^+$& -0.07$^+$&+0.18$^+$  &+0.0$^+$ & & & \SW{-2.4} & \SW{-3.5} & \\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{ADM} & & & & & & &  0.1 & -0.4 & \\
    \system{DM}    & & & & & & & 0.9 & 0.1 & \\
    \system{WDC}  & & & & & & & & & \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. For the Split experiments, we only report the loss in performance for the \domain{med} test set, (*) denote significant losses when domains are split or merged; (+) denotes a significant improvement over \system{Full FT}; \fyTodo{How about wrong ?}}
  \label{tab:redomains}
\end{table}

@@

It is finally interesting to note that all systems, but \system{MDL Res}, are quite robust to domain merge: we see even small gains in performance (eg.\ for \system{DM}). While robustness is generally a good thing, it is also a sign of a poor overall usage of domain labels. \system{MDL Res}\fyTodo{To be completed}

@@

\subsubsection{Coping with a growing number of domains}
Another series of experiments evaluate the ability to handle additional domains (requirement [P6-DYN]) as follows. Starting with the existing MDMT systems of Section~\ref{ssec:rawperformance}, we introduce an additional domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is again of utmost importance for achieving optimal performance: since our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy where. This is of course detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation}. We contrast this approach with retraining all the systems from scratch, and report the difference in performance in Table~\ref{tab:warmrestart}.
We expect that a good MDMT system should not be significantly affected by the addition of a new domain, and reach about the same performance as if the training included this domain from scratch. Note that from a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{TTC} or \system{DC-Feat} where new domains merely add new labels. It is less simple for \system{LDC} and \system{MDL~Res}\fyTodo{Complete effects of new domain}, for which the number of possible domains is built in the architecture and has to be anticipated from the begining. This makes another difference between domain-bounded MT-systems, for which the number of possible domains is upper bounded and truely open-domain systems.% , which seamlessly integrate additional domains.

@@

The multi-domain training regime is more the norm than the exception for NLP \cite{Dredze08online,Finkel09hierarchical}. We focus here mostly on multi-domain learning in machine translation, keeping in mind that similar problems and solutions (parameter sharing, instance selection and weighting, adversarial training, etc) have also been proposed for most language processing tasks.
%; scores are reported separately per domain, suggesting that all domains are equally important at test time.
% Adversarial adpatation is used in many domains
% for QA @misc{lee2019domainagnostic,
%    title={Domain-agnostic Question-Answering with Adversarial Training},
%    author={Seanie Lee and Donggyu Kim and Jangwon Park},
%    year={2019},
%    eprint={1910.09342},
%    archivePrefix={arXiv},
%    primaryClass={cs.CL}
%}, NLU and many others

Multi-domain translation was introduced for statistical MT (eg.\ \cite{Banerjee10combining,Sennrich13multidomain}): as for domain adaptation, two main strategies where considered consisting at weighting train and test instances based on their domain-relatedness on the one hand; or to inject domain labels as additional features in learning.

This latter strategy has also been widely used in MNT: the authors of \cite{Kobus17domaincontrol} inject an additional domain feature in their seq2seq model, either in the form of an extra (initial) domain-token, or in the form of additional domain-feature associated to each word. Note his technique has also been used to control the style of MT outputs in \cite{Sennrich16politeness,Niu18multitask}, and to encode the source or target languages in multilingual MT \cite{Firat16multiway,Johnson17google}. This approach is extended in \cite{Pham19generic} where source word embeddings are likely to vary across domains: this is achieved by splitting the embedding vector into a generic and a domain-specific part (one for each possible domain); a similar approach, applied to hidden states, is documented in \cite{Chu18multilingual}. Such feature-based approaches strongly rely on earlier proposals from the era of statistical MT \cite{Daume07frustratingly,Clark12onesystem}. Domain control can also be performed on the target side, as in \cite{Chen16guided}, where a vector of topic describing the current document is included as an extra context in the softmax layer of the decoder.

In \cite{Britz17mixing}, several methods are considered which aim to ensure that domain information is actually used in a mix-domain system. Three alternatives are considered, using either domain classification (or domain normalization, via adversarial training) on source or target representations. There is no clear winner in either of their three language pairs considered, which only distinguish a limited number of domains. The same basic techniques are simultaneously at play in \cite{Zeng18multidomain,Su19exploring}: in this approach, the upper layers of the MT aimed to sort out domain specific information on the one hand, and domain-agnostic information on the other hand, using auxiliary classification tasks, hoping that the domain-specific part will capture specific peculiarities of a domain, while the domain-agnostic part will be useful across the board. These techniques are implemented in an attentional sequence-to -sequence architecture in \cite{Zeng18multidomain}, and in Transformers in \cite{Su19exploring}.

A slightly more complex parameter-sharing scheme is presented in \cite{Jiang19multidomain}, which augments a transformer model with domain specific heads, whose individual contributions are regulated at the word (position-level): some words have ``generic'' use and rely on mixed-domain heads, while for some other words it is preferable to use domain specific heads. The results for three language pairs outperform several standard baselines for a 2-domain systems (in fr:en and ge:en) and a 4-domain system (zh:en).% \footnote{The reported results for WDC+WL are very bad, worst than anything \fyTodo{This is a mystery to me}.}

The work of \cite{Tars18multidomain} makes a good case against fine-tuning, which is often found to be too brittle, a defect that MDMT can fix, delivering superior generalization accuracy. They perform experiment with reference domain tags, using mostly the domain-control approach. They also report results obtained with automatically induced domain tags, which show that working with automatically induced tags (at the sentence level) is a viable alternative to using corpus labels as domain tags, a result that we have confirmed in section~\ref{}.

\newcite{Farajian17multidomain} also used automatic domains, performing on-line adaptation at the sentence-level. In their approach, the processing of a test sentence triggers the selection of a dedicated (small) set of fine-tuning instances assumed to be similar to the input text; using these, the generic NMT system is then tuned for some epochs, before delivering its translation. Different of most approaches studied here, this approach entirely dispenses with the notion of a domain, relying primarily on data selection/weighting techniques to handle data heterogeneity.

@@

>>>>

\section{Requirements of multi-domain MT \label{sec:requirements}}
In this section, we try to recap the main reasons for considering a multi-domain scenario and discuss their implications in terms of performance evaluation.
\fyDone{Relation to theory, discussion of worst case scenario}
\fyDone{Insist on the work of Dredze}

\subsection{Formalizing multi-domain translation \label{ssec:formalization}}

@@

A typical learning scenario in MT is to have access to a samples from $n_d$ domains, which means that the training distribution $\mathcal{D}^s$ is a mixture $\mathcal{D}^s(x) = \sum_d \lambda^{s}_{d} \mathcal{D}_d(x)$. Multi-domain learning, as defined in \cite{Dredze08online} further assumes that domain tags are also available in testing; the implication being that the test distribution is also as a mixture $\mathcal{D}^t(x) = \sum_d \lambda^{t}_{d} \mathcal{D}_d(x)$ of several domains, making the problem distinct from mere domain adaption.  A multi-domain learner is then expected to use these tags effectively \cite{Joshi12multidomain} when computing the combined translation function $h(x,d)$, and to perform well in all domains \cite{Finkel09hierarchical}. Note that this setting is closely related to the multi-source adaptation problem formalized in \cite{Mansour09domainadaptation,Mansour09multiple,Hoffman18algorithms}.

This definition seems to be the most accepted view of a multi-domain MT\footnote{One important exception is \cite{Farajian17multidomain}, where test translations rely on a similarity scores between test and train sentences, rather than on domain labels.} and one that we also adopt here. Note that in the absence of further specification, the naive answer to the MD setting should be to estimate one translation function $\hat{h}_d(x)$ separately for each domain, then to translate using $\hat{h}(x,d) = \sum_{d'} h_{d'}(x) \indic{d' = d}$, where $\indic{x}$ is the indicator function. We now discuss the arguments that are usually put forward to proceed differently.
% --

@@

Combining multiple domain-specific MTs can also be justified in the sake of distributional robustness \cite{Mansour09domainadaptation,Mansour09multiple}, for instance when the test mixture differs from the train mixture, or when it includes new domains unseen in training. Such scenario is already well documented for zero-shot multi-lingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}, where mixing languages has more than demonstrated its usefulness.  An even more challenging case is when the MT would need to perform well for any test distribution (as studied for statistical MT in \cite{Huck15mixeddomain}). In all these cases, mixing domains in training and/or testing is likely to improve robustness against unexpected or adversarial inputs \cite{,Oren19distributionally}.

@@

% \cite[eq. (3)]{Wang20general} defines the loss of MDMT as the (macro) average of domain loss - all domains are equally important.
\section{Challenging multi-domain translation systems \label{sec:challenging}}
In this section, we discuss seven\fyTodo{check number} operational requirements that can be expected from an effective multi-domain system, and discuss ways to evaluate whether these requirements are actually met. All these evaluations will rest on comparison of translation performance, and do not depend on the choice a particular metrics. To make our results comparable with the literature, we will only use the BLEU score \cite{Papineni02bleu} in Section~\ref{sec:experiments}, noting it may not be the best choice to measure subtle improvements of lexical choices that are often associated with domain adapted systems \cite{Irvine13measuring}. Other important figure of merits for MDMT systems are the computational cost and the total number of parameters.\fyDone{Insert discussion about scores}

@@

We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \cite{Papineni02bleu}.\\footnote{We use multibleu}fyDone{A word about meta-parameter settings}. Significance tests are performed using the bootstrap resampling method of \newcite{Koehn04statistical} and implementation of compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \cite{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value}

@@

\begin{table}
  \centering
  \begin{tabular}{|p{2.5cm}|*{9}{r|}} \hline
    % &&&&&& \\
    \hfill Set-up & \multicolumn{2}{c|}{Split} &  \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Split} & \multicolumn{2}{c|}{Merge} & Wrong \\ % \hline
     Model \hfill & \multicolumn{2}{c|}{\domain{med} \footnotesize{(0.5 / 0.5)}} &  \multicolumn{2}{c|}{\domain{med} {\footnotesize (0.25 / 0.75)}} & \multicolumn{2}{c|}{\domain{bank} {\footnotesize (0.5 / 0.5)}} & \multicolumn{2}{c|}{\domain{bank}+\domain{law}} & domain \\ \hline
    & \domain{med}$_1$ & \domain{med}$_2$ & \domain{med}$_1$ & \domain{med}$_1$ &  \domain{bank}$_1$ & \domain{bank}$_2$ & \domain{bank} & \domain{law} & \\
    \system{FT-Full}      & -0.13 & -0.6 & -1.51& -0.25& & &\SW{-1.6} & \SW{-1.4}& \\
    \system{DC-Tag}     & -0.16 & -0.27& +0.13& +0.2& & & -0.5 & -0.4 & \\
    \system{DC-Feat}    & -0.47& 0.0 & \SB{0.27} $^+$ & +0.27 $^+$& & & 0.3 & 0.1 & \\
    \system{TTM}          & & & & & & &  0.0 & -0.3 &  \\
    \system{LDC-Tag}   & & & & & & &  0.0 & 0.1& \\ 
    \system{MDL Res}   & -0.2$^+$& -0.07$^+$&+0.18$^+$  &+0.0$^+$ & & & 0.7 & -0.3 & \\
%    \system{MDL Gated} & & & & & & & & &  \\
    \system{ADM} & & & & & & &  0.1 & -0.4 & \\
    \system{DM}    & & & & & & & 0.9 & 0.1 & \\
    \system{WDC}  & & & & & & & & & \\
    \hline
  \end{tabular}
  \caption{Translation performance with variable domain definitions. For the Split experiments, we only report the loss in performance for the \domain{med} test set, (*) denote significant losses when domains are split or merged; (+) denotes a significant improvement over \system{Full FT}; \fyTodo{How about wrong ?}}
  \label{tab:redomains}
\end{table}

@@

It is finally interesting to note that all systems are quite robust to domain merge: we even see some small gains in performance (eg.\ for \system{DM}). While robustness is generally a good thing, it is also a sign of a poor overall usage of domain labels. \fyTodo{To be completed}

@@

\subsubsection{Coping with a growing number of domains}
Another series of experiments evaluate the ability to handle additional domains (requirement [P6-DYN]) as follows. Starting with the existing MDMT systems of Section~\ref{ssec:rawperformance}, we introduce an additional domain (\domain{News}) and resume training with this new mixture of data\footnote{The design of a proper balance between domains in training is again of utmost importance for achieving optimal performance: since our goal is to evaluate all systems in the same conditions, we consider a basic mixing policy where. This is of course detrimental to the small domains, for which the ``negative transfer'' effect is stronger than for larger domains.} for 50,000 additional iterations.\fyDone{Training regime of continuation}. We contrast this approach with retraining all systems from scratch and report differences in performance in Table~\ref{tab:warmrestart}.
We expect that a good MDMT system should not be significantly affected by the addition of a new domain, and reach about the same performance as if the training included this domain from scratch. Note that from a practical viewpoint, dynamically integrating new domains is straightforward for \system{DC-Tag}, \system{TTC} or \system{DC-Feat} where new domains merely add new labels. It is less simple for \system{LDC} and \system{MDL~Res}\fyTodo{Complete effects of new domain}, for which the number of possible domains is built in the architecture and has to be anticipated from the begining. This makes another difference between domain-bounded MT-systems, for which the number of possible domains is upper bounded and truely open-domain systems.% , which seamlessly integrate additional domains.

@@

The multi-domain training regime is more the norm than the exception for NLP \cite{Dredze08online,Finkel09hierarchical}. Our systematic study of domain use in MDMT owes much to the study of MD opinion mining systems of \newcite{Joshi12multidomain}. We focus here mostly on MD machine translation, keeping in mind that similar problems and solutions (parameter sharing, instance selection and weighting, adversarial training, etc) have also been proposed for most language processing tasks.
%; scores are reported separately per domain, suggesting that all domains are equally important at test time.
% Adversarial adpatation is used in many domains
% for QA @misc{lee2019domainagnostic,
%    title={Domain-agnostic Question-Answering with Adversarial Training},
%    author={Seanie Lee and Donggyu Kim and Jangwon Park},
%    year={2019},
%    eprint={1910.09342},
%    archivePrefix={arXiv},
%    primaryClass={cs.CL}
%}, NLU and many others

Multi-domain translation was already proposed for statistical MT (eg.\ \cite{Banerjee10combining,Clark12onesystem,Sennrich13multidomain,Huck15mixeddomain}): as for domain adaptation, two main strategies where considered consisting at weighting train and test instances based on their domain-relatedness on the one hand; or to inject domain labels as additional features in learning.

This latter strategy has also been widely used in MNT: the authors of \cite{Kobus17domaincontrol} inject an additional domain feature in their seq2seq model, either in the form of an extra (initial) domain-token, or in the form of additional domain-feature associated to each word. These results are reproduced in \cite{Tars18multidomain}, which also considers, as we do, automatically induced domain tags. Such technique also helps control the style of MT outputs in \cite{Sennrich16politeness,Niu18multitask}, and to encode the source or target languages in multilingual MT \cite{Firat16multiway,Johnson17google}. Domain control can also be performed on the target side, as in \cite{Chen16guided}, where a vector of topic describing the current document is included as an extra context in the softmax layer of the decoder. Such feature-based approaches strongly rely on earlier proposals from the era of statistical MT \cite{Daume07frustratingly,Clark12onesystem}.
Such ideas are further developed in \cite{Chu18multilingual,Pham19generic}, where domain differences and commonalties are encoded in the network architecture: some parameters are shared across domains (the recurrent layers and the attention in \cite{Pham19generic}), while others are domain-specific (part of the embeddings in \cite{Pham19generic}).

The techniques introduced in \cite{Britz17mixing} aim to ensure that domain information is actually used in a mix-domain system. Three alternatives are considered, using either domain classification (or domain normalization, via adversarial training) on source or target representations. There is no clear winner in either of their three language pairs considered, which only distinguish a limited number of domains. One contribution of this work was to introduce the idea of normalizing representations through adversarial training, so has to make the mixture of heterogeneous data more effective; representation normalization has since proven a key ingredient in multilingual transfer learning.
The same basic techniques (partial parameter sharing, automatic domain identification / normalization) are simultaneously at play in \cite{Zeng18multidomain}: in this approach, the lower layers of the MT use auxiliary classification tasks to disentangle domain specific representations on the one hand from domain-agnostic representation on the other hand. These representations are then processed as two separate inputs, then recombined to compute the translation. These techniques are extended and ported to the Transformer model by \newcite{Su19exploring}.

A slightly more complex parameter-sharing scheme is presented in \cite{Jiang19multidomain}, which augments a Transformer model with domain specific heads, whose individual contributions are regulated at the word (position-level): some words have ``generic'' use and rely on mixed-domain heads, while for some other words it is preferable to use domain specific heads, thereby reintroducing the idea of ensembling that is used in \cite{Huck15mixeddomain,Saunders19ucam}. The results for three language pairs outperform several standard baselines for a two-domain systems (in fr:en and ge:en) and a 4-domain system (zh:en).% \footnote{The reported results for WDC+WL are very bad, worst than anything \fyTodo{This is a mystery to me}.}

As already explained, \newcite{Farajian17multidomain} differs from most studies, as it does not use domain labels. In their approach, the processing of a test sentence triggers the selection of a dedicated (small) set of fine-tuning instances assumed to be similar to the input text; using these, the generic NMT system is then tuned for some epochs, before delivering its translation. This approach entirely dispenses with the notion of a domain, and primarily relies on data selection/weighting techniques to handle data heterogeneity.

@@

Multi-domain learning, as defined in \cite{Dredze08online} additionally makes the requirement that categorial domain tags are available in training and testing; a multi-domain learner should use them effectively \cite{Joshi12multidomain} to improve simultaneously on all domains \cite{Finkel09hierarchical}. This is also the view that we adopt here, where we assume training inputs in $(\mathcal{X}\times{}\{1\dots{}D\})$, sampled from a mixture $\sum \lambda_{s,d}\mathcal{D}_{d} \times \{d\}$, and also consider various test scenarios, depending whether $\mathcal{D}_t$ is a fixed mixture of known domains, include new domain(s), in the supervised and unsupervised, and zero-shot settings.\fyDone{explain zero shot}.
% ----
